Memories of migrations past: Sociality and cognition in dynamic, seasonal environments

### 2021-07-15 text/SocialMemoryMigration_FEE.tex
...

Migratory species are often considered to be more vulnerable to environmental change, as a disruption in either of the seasonal ranges or along a migratory corridor can have significant negative impacts \citep{Wilcove2008, Kauffman2021}. On the other hand, migratory species might be more resilient to disruptions due to their wide-ranging mobility \citep{Robinson2009}. Clearly, the ability to perform a migration without local cues is only possible if the behavior is hard-programmed or remembered. On the other hand, a strictly programmed behavior can be maladaptive if conditions change. Because the scenarios underlying migration are manifold and complex, mathematical modeling may provide some insights and help clarify where, when, and under what conditions we might migration behavior to emerge, to be adaptive, to be maladaptive, or to collapse.

>>>>

Whether long distance migration is a Migratory species are often considered to be more vulnerable to environmental change as disruption in either of the seasonal ranges or along a migratory corridor can have significant negative impacts \citep{Wilcove2008, Kauffman2021}. On the other hand, migratory species might be more resilient to large-scale disruptions due to their wide-ranging mobility \citep{Robinson2009}. Clearly, the ability to perform a migration without local cues is only possible if the behavior is hard-programmed or remembered. On the other hand, a strictly programmed behavior can be maladaptive if conditions change. Because the scenarios underlying migration are manifold and complex, mathematical modeling may provide some insights and help clarify where, when, and under what conditions we might migration behavior to emerge, to be adaptive, to be maladaptive, or to collapse.
